### 2021-04-07 outputs/paper/paper.Rmd
Edit data cleaning code

---
title: "The Impact on Job Interest of Beginner Programmers in the Tech Sector"
subtitle: "TBD"
author: "TBD"
thanks: "https://github.com/bonjwow/new-coders"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

# Introduction

# Data

# Model

# Results

# Discussion
```{r, include=FALSE}
### TODO's
# Write at least 2.5 pages for the Discussion section
# Weaknesses and next steps
```

\newpage

# Appendix {-}

\newpage

# References

### 2021-04-07 scripts/01-data_cleaning.R

@@ -8,10 +8,70 @@
 #### Workspace setup ####
 library(haven)
 library(tidyverse)
-# Read in the raw data. 
+library(dplyr)
+
+#### Get data ####
 raw_data <- readr::read_csv("https://raw.githubusercontent.com/freeCodeCamp/2017-new-coder-survey/ed8a2c5118209fa26cc823fd33fedcf6fe5661ec/clean-data/2017-fCC-New-Coders-Survey-Data.csv")
 
-         
+#### Clean data ####
+dfClean <-
+  raw_data %>%
+  select('Age',
+         'CityPopulation',
+         'CommuteTime',
+         'Gender',
+         'Income',
+         'MoneyForLearning',
+         'MonthsProgramming',
+         'SchoolDegree') %>%
+  ### Recode
+  mutate(CityPopulation = dplyr::recode(CityPopulation,
+                                     "less than 100,000" = 0,
+                                     "between 100,000 and 1 million" = 1,
+                                     "more than 1 million" = 2,
+                                     .default = 999)) %>%
+  mutate(CommuteTime = dplyr::recode(CommuteTime,
+                                     "I work from home" = 0,
+                                     "Less than 15 minutes" = 1,
+                                     "15 to 29 minutes" = 2,
+                                     "30 to 44 minutes" = 3,
+                                     "45 to 60 minutes" = 4,
+                                     "More than 60 minutes" = 5,
+                                     .default = 999)) %>%
+  mutate(Gender = dplyr::recode(Gender,
+                                "male" = 0,
+                                "female" = 1,
+                                .default = 999)) %>%
+  mutate(SchoolDegree = dplyr::recode(SchoolDegree,
+                                "no high school (secondary school)" = 0,
+                                "some high school" = 0,
+                                "high school diploma or equivalent (GED)" = 0,
+                                "trade, technical, or vocational training" = 0,
+                                "some college credit, no degree" = 1,
+                                "associate's degree" = 1,
+                                "bachelor's degree" = 2,
+                                "master's degree (non-professional)" = 3,
+                                "professional degree (MBA, MD, JD, etc.)" = 3,
+                                "Ph.D." = 4,
+                                .default = 999)) %>%
+  ### Remove empty rows
+  mutate_all(~ifelse(. %in% c(999, "N/A", "null", ""), NA, .)) %>%
[…]

### 2021-04-07 outputs/paper/paper.Rmd
Add correlation analysis

@@
 ---
-title: "The Impact on Job Interest of Beginner Programmers in the Tech Sector"
+title: "The Impact on Job Interest of Beginner Programmers"
 subtitle: "TBD"
@@
 library(tidyverse)
+library(dplyr)
+library(stargazer)
+library(psych)
+library(PerformanceAnalytics)
 ```
@@
 # Data
+```{r}
+#### Message ####
+# Show code for reviewers
+#
+# // Variables
+# Y: MoneyForLearning
+# X: Age, CityPopulation, CommuteTime, Income, MonthsProgramming, SchoolDegree
+# c: Gender
+# 
+# // Clean csv
+# https://github.com/bonjwow/new-coders/blob/main/inputs/data/clean_new-coders.csv
+#
+#
+
+#### Get data ####
+dfNewCoders <- 
+  readr::read_csv("../../inputs/data/clean_new-coders.csv")
+
+```
+
+```{r}
+#### Descriptive statistics ####
+stargazer::stargazer(data.frame(dfNewCoders), type="text")
+
+```
+
+```{r}
+#### Test internal consistency with Cronbach's alpha ####
+psych::alpha(dfNewCoders)
+```
+
+```{r}
+#### Correlation analysis ####
+
+### Print correlation coefficient
+round(cor(dfNewCoders), 3)
+
+```
+
+```{r}
+### Print correlation matrix
+PerformanceAnalytics::chart.Correlation(dfNewCoders, 
+                                        histogram = TRUE, 
+                                        pch = 19)
+```
 
@@
 ```{r, include=FALSE}
-### TODO's
+#### TODO's ####
 # Write at least 2.5 pages for the Discussion section

### 2021-04-08 outputs/paper/paper.Rmd
Add regression model

@@
 library(psych)
+# install.packages("PerformanceAnalytics")
 library(PerformanceAnalytics)
+# install.packages("QuantPsyc")
+library(QuantPsyc)
+library(car)
 ```
@@
 # Data
+```{r, include=FALSE}
+#### TODO's ####
+# Explain raw data 
+#
+```
+
 ```{r}
@@
 ```{r}
-#### Test internal consistency with Cronbach's alpha ####
-psych::alpha(dfNewCoders)
-```
-
-```{r}
 #### Correlation analysis ####
@@
 # Model
+```{r, include=FALSE}
+#### TODO's ####
+# Write out what each variable is
+# Weaknesses and next steps
+```
+
+```{r}
+#### Multiple regression analysis ####
+summary(fit.lm <- lm(formula = 
+                       MoneyForLearning ~ 
+                       Gender +
+                       CityPopulation +
+                       CommuteTime +
+                       Income +
+                       MonthsProgramming +
+                       SchoolDegree, 
+                     data = dfNewCoders))
+```
+```{r}
+#### Beta ####
+QuantPsyc::lm.beta(fit.lm)
+```
+
+```{r}
+#### Check multicollinearity with Variance Inflation Factor (VIF) & Tolerance ####
+
+### VIF
+car::vif(fit.lm)
+### Tolerance
+1/car::vif(fit.lm)
+```
+
+```{r}
+
+```
 

### 2021-04-08 scripts/01-data_cleaning.R

@@ -54,6 +54,10 @@ dfClean <-
                                 "professional degree (MBA, MD, JD, etc.)" = 3,
                                 "Ph.D." = 4,
                                 .default = 999)) %>%
+  ### Relocate columns
+  dplyr::relocate(Gender, .before = Age) %>%
+  dplyr::relocate(MoneyForLearning, .after = SchoolDegree) %>%
+  
   ### Remove empty rows
   mutate_all(~ifelse(. %in% c(999, "N/A", "null", ""), NA, .)) %>%
   na.omit()

### 2021-04-10 outputs/paper/paper.Rmd
Add introduction

@@
 ---
-title: "The Impact on Job Interest of Beginner Programmers"
-subtitle: "TBD"
-author: "TBD"
+title: "The Impact of Education Expenditure of New Coders"
+subtitle: "The Factors Affecting Education Costs of Beginner Programmers to Learn to Code aside from University Tuition"
+author: "Bongju Yoo"
 thanks: "https://github.com/bonjwow/new-coders"
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: ""
 output:
@@
 
+With an increasing interest in computer programming and the growth of coding related jobs, more and more people invest their time and money in taking programming courses [@citeHughes].
+In this paper, I examine some of the factors that may affect educational expenditure of new coders or entry-level programmers aside from university tuition, mainly focusing on the level of education, the size of city, commuting time, income, and learning time.
+The dataset used for this paper is obtained from freeCodeCamps GitHub page ^[https://github.com/freeCodeCamp/2017-new-coder-survey].
+Approximately 20,000 beginner programmers had participated in the survey [@citeSurvey2017].
+
+Firstly, I processed correlation analysis to identify the relationship between each independent variable and dependent variable (education costs) pair and found that all the pairs have a positive linear relationship except for commuting time.
+Secondly, I used multiple linear regression to determine the statistical significance of the factors.
+The result of the analysis shows that commuting time is not statistically significant.
+Interestingly, education background is also not statistically significant associated with educational expenditure of beginner programmers.
+Other variables, such as the size of city, income, and learning time, have a statistical significance on the costs.
+
+This analysis shows that beginner programmers living in small towns and/or low-income households are likely to spend less money on learning to code aside from university tuition than those who live in bigger cities and/or high-income households.
+It is assumed that there is still a lack of educational resources for new coders living in rural areas and/or low-income households.
+Free online learning platforms such as freeCodeCamp can be a great resource of education for the coders.
+
+The paper is organized as follows.
+The Data section describes features of the original survey data and how the data is preprocessed.
+The Model section explains the multiple linear regression model used to assess the association between each factor and educational expenditure of beginner programmers, and evaluates the model using its residual standard error, multiple R-squared, and F-statistic.
+The Results section summarises the results of the regression model and model evaluation processes in the Model section.
+Lastly, the Discussion section discusses the findings and potential limitations of the paper, and suggests directions for future research related to this data.
+
 # Data
@@
 ```{r}
-#### Message ####
-# Show code for reviewers
+#### Message to Reviewers ####
+#
+# Code chunks are visible on the PDF for the review.
+# Any comments or suggestions are welcome to improve this paper :D
 #
@@
 # c: Gender
-# 
-# // Clean csv
-# https://github.com/bonjwow/new-coders/blob/main/inputs/data/clean_new-coders.csv
-#
 #

### 2021-04-10 outputs/paper/paper.Rmd
Add introduction

@@
 ---
-title: "The Impact of Education Expenditure of New Coders"
+title: "The Impact of Educational Expenses of New Coders"
 subtitle: "The Factors Affecting Education Costs of Beginner Programmers to Learn to Code aside from University Tuition"
@@
 With an increasing interest in computer programming and the growth of coding related jobs, more and more people invest their time and money in taking programming courses [@citeHughes].
-In this paper, I examine some of the factors that may affect educational expenditure of new coders or entry-level programmers aside from university tuition, mainly focusing on the level of education, the size of city, commuting time, income, and learning time.
+In this paper, I examine some of the factors that may affect educational expenses of new coders or entry-level programmers aside from university tuition, mainly focusing on the level of education, the size of city, commuting time, income, and learning time.
 The dataset used for this paper is obtained from freeCodeCamps GitHub page ^[https://github.com/freeCodeCamp/2017-new-coder-survey].
@@
 The result of the analysis shows that commuting time is not statistically significant.
-Interestingly, education background is also not statistically significant associated with educational expenditure of beginner programmers.
+Interestingly, education background is also not statistically significant associated with educational expenses of beginner programmers.
 Other variables, such as the size of city, income, and learning time, have a statistical significance on the costs.
@@
 The Data section describes features of the original survey data and how the data is preprocessed.
-The Model section explains the multiple linear regression model used to assess the association between each factor and educational expenditure of beginner programmers, and evaluates the model using its residual standard error, multiple R-squared, and F-statistic.
+The Model section explains the multiple linear regression model used to assess the association between each factor and educational costs of beginner programmers, and evaluates the model using its residual standard error, multiple R-squared, and F-statistic.
 The Results section summarises the results of the regression model and model evaluation processes in the Model section.

### 2021-04-14 outputs/paper/paper.Rmd
Add the  package

@@
 library(psych)
+# install.packages("here")
+library(here)
 # install.packages("PerformanceAnalytics")
@@
 dfNewCoders <- 
-  readr::read_csv("../../inputs/data/clean_new-coders.csv")
+  readr::read_csv(here::here("inputs/data/clean_new-coders.csv"))
 

### 2021-04-15 outputs/paper/paper.Rmd
Edit correlation matrix table

@@
 library(car)
+library(kableExtra)
+```
+
+```{r, include=FALSE}
+# Source: https://stefaneng.github.io/apa_correlation_table/
+# install.packages("Hmisc")
+library(Hmisc)
+
+apply_if <- function(mat, p, f) {
+  # Fill NA with FALSE
+  p[is.na(p)] <- FALSE
+  mat[p] <- f(mat[p])
+  mat
+}
+
+apaCorr <- function(mat, corrtype = "pearson") {
+  matCorr <- mat
+  if (class(matCorr) != "rcorr") {
+    matCorr <- rcorr(mat, type = corrtype)
+  }
+  # Add one star for each p < 0.05, 0.01, 0.001
+  stars <- apply_if(round(matCorr$r, 2), matCorr$P < 0.05, function(x) paste0(x, "*"))
+  stars <- apply_if(stars, matCorr$P < 0.01, function(x) paste0(x, "*"))
+  stars <- apply_if(stars, matCorr$P < 0.001, function(x) paste0(x, "*"))
+  # Put - on diagonal and blank on upper diagonal
+  stars[upper.tri(stars, diag = T)] <- "-"
+  stars[upper.tri(stars, diag = F)] <- ""
+  n <- length(stars[1,])
+  colnames(stars) <- 1:n
+  # Remove _ and convert to title case
+  row.names(stars) <- tools::toTitleCase(sapply(row.names(stars), gsub, pattern="_", replacement = " "))
+  # Add index number to row names
+  row.names(stars) <- paste(paste0(1:n,"."), row.names(stars))
+  stars
+}
 ```
@@
 # Explain raw data 
+# Discuss the variables
 #
@@
 
-```{r}
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
 #### Descriptive statistics ####
-stargazer::stargazer(data.frame(dfNewCoders), type="text")
+stargazer::stargazer(data.frame(dfNewCoders), type = "text")
 
@@
 
-```{r}
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
 #### Correlation analysis ####
@@
 ### Print correlation coefficient
-round(cor(dfNewCoders), 3)
+tblCorr <-
+  dfNewCoders %>%
+  as.matrix() %>%
+  apaCorr() %>%
+  data.frame() %>%
+  kable(caption = "Correlation matrix for variables",
+        booktabs = TRUE,
+        col.names = c("1", "2", "3", "4", "5", "6","7","8")) %>%
+  footnote(general = "* p < 0.05, ** p < 0.01, *** p < 0.001",
+             general_title = "")
+
+tblCorr
 

### 2021-04-16 outputs/paper/paper.Rmd
Edit regression model table

@@
         booktabs = TRUE,
-        col.names = c("1", "2", "3", "4", "5", "6","7","8")) %>%
+        col.names = c("1", "2", "3", "4", "5", "6", "7", "8")) %>%
   footnote(general = "* p < 0.05, ** p < 0.01, *** p < 0.001",
@@
 
-```{r}
+```{r, results='asis'}
 #### Multiple regression analysis ####
-summary(fit.lm <- lm(formula = 
+fit.lm <- lm(formula = 
                MoneyForLearning ~ 
@@
                SchoolDegree, 
-                     data = dfNewCoders))
+               data = dfNewCoders)
+
+# summary(fit.lm)
+stargazer::stargazer(fit.lm, 
+          title = "Result of regression model", 
+          header = FALSE,
+          type = "latex")
 ```
+
 ```{r}
@@
 ```{r}
-
+# TODO: RMSE
 ```

### 2021-04-17 outputs/paper/paper.Rmd
Edit regression analysis

@@
 #### Multiple regression analysis ####
-fit.lm <- lm(formula = 
+multiReg1 <- lm(formula = 
                MoneyForLearning ~ 
-               Gender +
                CityPopulation +
@@
 
-# summary(fit.lm)
-stargazer::stargazer(fit.lm, 
+multiReg2 <- lm(formula = 
+               MoneyForLearning ~ 
+               Age +
+               CityPopulation +
+               CommuteTime +
+               Income +
+               MonthsProgramming +
+               SchoolDegree, 
+               data = dfNewCoders)
+
+multiReg3 <- lm(formula = 
+               MoneyForLearning ~ 
+               Gender +
+               Age +
+               CityPopulation +
+               CommuteTime +
+               Income +
+               MonthsProgramming +
+               SchoolDegree, 
+               data = dfNewCoders)
+
+# summary(multiReg3)
+stargazer::stargazer(multiReg1, multiReg2, multiReg3, 
           title = "Result of regression model", 
@@
 #### Beta ####
-QuantPsyc::lm.beta(fit.lm)
+QuantPsyc::lm.beta(multiReg3)
 ```
@@
 ### VIF
-car::vif(fit.lm)
+car::vif(multiReg3)
 ### Tolerance
-1/car::vif(fit.lm)
+1/car::vif(multiReg3)
 ```

### 2021-04-18 outputs/paper/paper.Rmd
Add a table for the cleaned dataset

@@
 library(dplyr)
+library(janitor)
 library(stargazer)
@@
 # Data
-```{r, include=FALSE}
-#### TODO's ####
-# Explain raw data 
-# Discuss the variables
-#
-```
 
-```{r}
-#### Message to Reviewers ####
-#
-# Code chunks are visible on the PDF for the review.
-# Any comments or suggestions are welcome to improve this paper :D
-#
-# // Variables
-# Y: MoneyForLearning
-# X: Age, CityPopulation, CommuteTime, Income, MonthsProgramming, SchoolDegree
-# c: Gender
-#
-
+```{r table1, echo=FALSE, warning=FALSE, message=FALSE}
 #### Get data ####
@@
 ```
+
+## Description of Dataset
+The original dataset used for this paper is obtained from `freeCodeCamp`’s GitHub page.
+The format of the dataset is a comma-separated values (CSV) file, which contains 136 columns and 18,175 observations.
+I selected 8 variables and cleaned the data using the R programming language [@citeR] and the tidyverse package [@cityTidyverse] and the dplyr package [@cityDplyr].
+The selected variables are: Age, CityPopulation, CommuteTime, Gender,  Income,  MoneyForLearning,  MonthsProgramming, and SchoolDegree.
+The CityPopulation is the estimated number of city population of the recipient; the question asked was "About how many people live in your city?”, and there are three options to choose: “less than 100,000”,  "between 100,000 and 1 million", and "more than 1 million".
+Since these answers were coded as strings, I converted them into numeric variables using the `recode` function of `dplyr` [@cityDplyr].
+The answers for CommuteTime and SchoolDegree were also coded as strings in the original dataset, so I applied the same data cleaning process to the variables as I did with CityPopulation.
+Also, I omitted observations which have a missing value.
+Table \@ref(tab:tabViewDataset) is a partial view of the cleaned dataset after the preprocessing.
+
+```{r tabViewDataset, echo=FALSE, warning=FALSE, message=FALSE}
+#### A partial view of the cleaned dataset ####
+tableCleanedData <-
+  dfNewCoders[1:10,] %>%
+  mutate_all(linebreak) %>%
+  kable(caption = "A partial view of \\\\the cleaned dataset",
+      booktabs = T,
+      escape = F,
+      "latex",
+      col.names = linebreak(c("Gender", 
+                              "Age",
+                              "City\nPopulation",
+                              "Commute\nTime",
+                              "Income",
+                              "Months\nProgramming",
+                              "School\nDegree",
+                              "Money For\nLearning"), align = "c")) %>%
+  kable_classic(full_width = F)
+
+tableCleanedData
+
+```
+
+## Methodology and Data Collection
 

### 2021-04-18 outputs/paper/paper.Rmd
Edit a table for descriptive statistics

@@
 The format of the dataset is a comma-separated values (CSV) file, which contains 136 columns and 18,175 observations.
-I selected 8 variables and cleaned the data using the R programming language [@citeR] and the tidyverse package [@cityTidyverse] and the dplyr package [@cityDplyr].
+I selected 8 variables and cleaned the data using the R programming language [@citeR] and the `tidyverse` package [@cityTidyverse] and the `dplyr` package [@cityDplyr].
 The selected variables are: Age, CityPopulation, CommuteTime, Gender,  Income, MoneyForLearning, MonthsProgramming, and SchoolDegree.
@@
 #### A partial view of the cleaned dataset ####
-tableCleanedData <-
+tabCleanedData <-
   dfNewCoders[1:10,] %>%
@@
 
-tableCleanedData
+tabCleanedData
+
+```
+
+```{r tabDescrStat, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
+#### Descriptive statistics ####
+
+stargazer::stargazer(data.frame(dfNewCoders), 
+                     type = "latex", 
+                     title = "Descriptive statistics for the cleaned dataset", 
+                     header = FALSE,
+                     single.row = TRUE)
 
@@
 ## Methodology and Data Collection
-
-```{r, echo=FALSE, warning=FALSE, message=FALSE}
-#### Descriptive statistics ####
-stargazer::stargazer(data.frame(dfNewCoders), type = "text")
-
-```
 

### 2021-04-18 outputs/paper/paper.Rmd
Add model formulae

@@
 
-```{r}
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
 ### Print correlation matrix
@@
 
-```{r, results='asis'}
+## Formulae
+
+This equation \@ref(eq:linRegModel1) is a model formula for the regression model 1.
+
+\begin{equation}
+(\#eq:linRegModel1)
+Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \epsilon
+\end{equation}
+
+This equation \@ref(eq:linRegModel2) is a model formula for the regression model 2.
+
+\begin{equation}
+(\#eq:linRegModel2)
+Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \epsilon
+\end{equation}
+
+This equation \@ref(eq:linRegModel3) is a model formula for the regression model 3.
+
+\begin{equation}
+(\#eq:linRegModel3)
+Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \beta_6X_6 + \epsilon
+\end{equation}
+
+```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
 #### Multiple regression analysis ####
@@
                CityPopulation +
-               CommuteTime +
+               # CommuteTime +
                Income +

### 2021-04-18 outputs/paper/paper.Rmd
Add RMSE

@@
 library(kableExtra)
+# install.packages("forecast")
+library(forecast)
 ```
@@
 
-## Formulae
+## Model formulae
 
@@
 (\#eq:linRegModel1)
-Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \epsilon
+MoneyForLearning \sim \beta_0 + \beta_1 \times CityPopulation + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \epsilon
 \end{equation}
@@
 (\#eq:linRegModel2)
-Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \epsilon
+MoneyForLearning \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \epsilon
 \end{equation}
@@
 (\#eq:linRegModel3)
-Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \beta_6X_6 + \epsilon
+MoneyForLearning \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \beta_6X_6 + \epsilon
 \end{equation}
@@
 
+## Model validation
+```{r}
+#### Line plot for fitted values
+plot(dfNewCoders$MoneyForLearning)
+lines(multiReg1$fitted.values, col = "red")
+lines(multiReg2$fitted.values, col = "blue")
+lines(multiReg3$fitted.values, col = "green")
+
+```
+
+```{r}
+#### RMSE ####
+forecast::accuracy(multiReg1)
+```
+
+```{r}
+#### RMSE with custom function ####
+# Source: https://stackoverflow.com/questions/26237688/rmse-root-mean-square-deviation-calculation-in-r
+
+RMSE <- function(error) {
+  sqrt(mean(error^2)) 
+}
+
+RMSE(multiReg1$residuals)
+
+```
+
 ```{r}
@@
 1/car::vif(multiReg3)
-```
-
-```{r}
-# TODO: RMSE
 ```

### 2021-04-18 outputs/paper/paper.Rmd
Add custom function for RMSE

@@
 library(kableExtra)
-# install.packages("forecast")
-library(forecast)
 ```
@@
 
-## Model validation
-```{r}
-#### Line plot for fitted values
-plot(dfNewCoders$MoneyForLearning)
-lines(multiReg1$fitted.values, col = "red")
-lines(multiReg2$fitted.values, col = "blue")
-lines(multiReg3$fitted.values, col = "green")
-
-```
-
-```{r}
-#### RMSE ####
-forecast::accuracy(multiReg1)
-```
+## Model validation with RMSE
 
@@
 RMSE(multiReg1$residuals)
+RMSE(multiReg2$residuals)
+RMSE(multiReg3$residuals)
+
+# Model3 has the lowest RMSE among the 3 models => Model3 is the best!
 

### 2021-04-18 outputs/paper/paper.Rmd
Add data collection

@@
 In this paper, I examine some of the factors that may affect educational expenses of new coders or entry-level programmers aside from university tuition, mainly focusing on the level of education, the size of city, commuting time, income, and learning time.
-The dataset used for this paper is obtained from freeCodeCamps GitHub page ^[https://github.com/freeCodeCamp/2017-new-coder-survey].
 Approximately 20,000 beginner programmers had participated in the survey [@citeSurvey2017].
@@
 ```
+## Data Collection
+The survey was run by `freeCodeCamp`, a non-profit organization that helps people learn to code through their free online courses and build a network for their alumni [@citeAbout].
+The purpose of the survey was to examine how the users learn to code [@cite2017Survey].
+The survey was conducted over the internet, and the survey respondents were limited to those persons with less than 5 years learning programming; all the respondents were asked whether they have already been coding for more than 5 years or not before starting the survey [@cite2017Survey].
+The survey is composed of 48 questions and takes about five minutes to complete, and the survey results are under the Open Data Common License, which can be freely distributed through the organization’ GitHub repository [@cite2017Survey].^[https://github.com/freeCodeCamp/2017-new-coder-survey]
 
@@
   mutate_all(linebreak) %>%
-  kable(caption = "A partial view of \\\\the cleaned dataset",
+  kable(caption = "A partial view of the cleaned dataset",
       booktabs = T,
@@
 ```
+
+Table \@ref(tab:tabDescrStat) is
 

### 2021-04-19 outputs/paper/paper.Rmd
Add text for correlation analysis

@@
 
-Table \@ref(tab:tabDescrStat) is
+Table 2 displays descriptive statistics for the cleaned data after the preprocessing.
+The total number of observations is 7,022 and the data type for all variables are numeric variables.
+The median age of the respondents is 30 years and the median income of them is about \$43,000 in U.S.
+dollars.
+The average of the respondents has spent about 2 years and about \$1,000 in U.S.
+dollars learning to code.
 
@@
 #### Descriptive statistics ####
-
 stargazer::stargazer(data.frame(dfNewCoders), 
@@
 
-## Methodology and Data Collection
+## Correlation Analysis
 
-```{r, echo=FALSE, warning=FALSE, message=FALSE}
+I ran a correlation matrix to check correlation coefficients between the variables.
+To create the correlation matrix, I used a custom function written by Stefan Eng [@citeEng].
+His function contains the `Hmisc` package’s `rcorr` function to calculate the correlations with the p-values and display starts based on the significance level of each cell when the value is lower than a specific level [@citeHmisc].
+Along with his custom to compute the correlation matrix, I used the `kable` package to print out the result in a table format [@citeKable].
+As can be seen in Table \@ref(tab:tabCorrAnalysis), the result of the correlation matrix shows that all independent variables have a positive significant relationship with the dependent variable, MoneyForLearning, except for CommuteTime.
+This can be interpreted that a commuting time to work does not affect educational expenditure of new coders aside from their post-secondary education cost.
+
+```{r tabCorrAnalysis, echo=FALSE, warning=FALSE, message=FALSE}
 #### Correlation analysis ####

### 2021-04-20 outputs/paper/paper.Rmd
Edit model equations
Add regression model for city population

@@
 
-## Model formulae
+## Model Formulae
 
@@
 (\#eq:linRegModel1)
-MoneyForLearning \sim \beta_0 + \beta_1 \times CityPopulation + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \epsilon
+Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \epsilon
 \end{equation}
@@
 (\#eq:linRegModel2)
-MoneyForLearning \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \epsilon
+Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \epsilon
 \end{equation}
@@
 (\#eq:linRegModel3)
-MoneyForLearning \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \beta_6X_6 + \epsilon
+Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \beta_6X_6 + \epsilon
 \end{equation}
@@
 #### Multiple regression analysis ####
+
+### Run linear regression models
 multiReg1 <- lm(formula = 
                MoneyForLearning ~ 
-               CityPopulation +
-               # CommuteTime +
-               Income +
-               MonthsProgramming +
-               SchoolDegree, 
+               Income,
                data = dfNewCoders)
@@
                MoneyForLearning ~ 
-               Age +
+               # Gender +
+               # Age +
                CityPopulation +
@@
 stargazer::stargazer(multiReg1, multiReg2, multiReg3, 
-          title = "Result of regression model", 
+          title = "Predictions of money for learning across experimental conditions", 
           header = FALSE,
           type = "latex")
+```
+
+```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
+#### Multiple regression analysis (by city population) ####
+dfSmCity <-
+  dfNewCoders %>%
+  filter(CityPopulation == 0)
+
+dfMdCity <-
+  dfNewCoders %>%
+  filter(CityPopulation == 1)
+
+dfLgCity <-
+  dfNewCoders %>%
+  filter(CityPopulation == 2)
+
+### Run linear regression models
+linReg1 <- lm(formula = 
+               MoneyForLearning ~ 
+               Income,
+               data = dfNewCoders)
+
+linReg2 <- lm(formula = 
+               MoneyForLearning ~ 
+               Income,
+               data = dfSmCity)
+
+linReg3 <- lm(formula = 
+               MoneyForLearning ~ 
+               Income,
+               data = dfMdCity)
+
+linReg4 <- lm(formula = 
+               MoneyForLearning ~ 
+               Income,
+               data = dfLgCity)
+
+stargazer::stargazer(linReg1, linReg2, linReg3, linReg4,
+          title = "Predictions of money for learning by city population", 
+          header = FALSE,
+          type = "latex",
+          column.labels = c("Any", "Small", "Medium", "Large"),
+          font.size = "tiny")
+
 ```

### 2021-04-20 outputs/paper/paper.Rmd
Add model validation table

@@
 
-```{r}
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
 #### RMSE with custom function ####
+
+# Source: https://medium.com/dev-genius/metrics-for-evaluating-linear-regression-models-36df305510d9
 # Source: https://stackoverflow.com/questions/26237688/rmse-root-mean-square-deviation-calculation-in-r
 
-RMSE <- function(error) {
-  sqrt(mean(error^2)) 
+RSQ <- function(model) {
+  return(summary(model)$r.squared)
 }
 
-RMSE(multiReg1$residuals)
-RMSE(multiReg2$residuals)
-RMSE(multiReg3$residuals)
+MSE <- function(error) {
+  return(mean(error^2))
+}
 
+RMSE <- function(error) {
+  return(sqrt(mean(error^2))) 
+}
+
+vecModel <-
+  c("Model (1)", "Model (2)", "Model (3)")
+
+vecRSQ <- 
+  c(RSQ(multiReg1), RSQ(multiReg2), RSQ(multiReg3))
+
+vecMSE <-
+  c(MSE(multiReg1$residuals), MSE(multiReg2$residuals), MSE(multiReg3$residuals))
+
+vecRMSE <-
+  c(RMSE(multiReg1$residuals), RMSE(multiReg2$residuals), RMSE(multiReg3$residuals))
+
+dfModelValid <-
+  data.frame(vecModel, vecRSQ, vecMSE, vecRMSE) %>%
+  kable(caption = "Model validation",
+        booktabs = TRUE,
+        col.names = c("Model", "R-squared", "MSE", "RMSE")) %>%
+  column_spec(column = 1, width = "4cm") %>%
+  column_spec(column = 2:4, width = "3cm")
+
+dfModelValid
+
+# If R-squared is closer to 0 = Good!
 # Model3 has the lowest RMSE among the 3 models => Model3 is the best!

### 2021-04-21 outputs/paper/paper.Rmd
Edit model validation table
Edit model evaluation tables

@@
 ```{r, include=FALSE}
+#### Custom functions ####
+
+### Format number
+# Source: https://stackoverflow.com/questions/29465941/format-number-in-r-with-both-comma-thousands-separator-and-specified-decimals
+
+formatNumber <- function(numb, decimal) {
+  return(format(round(as.numeric(numb), decimal), nsmall=decimal, big.mark=",")) 
+}
+
+### APA style correlation matrix 
 # Source: https://stefaneng.github.io/apa_correlation_table/
@@
 stargazer::stargazer(multiReg1, multiReg2, multiReg3, 
-          title = "Predictions of money for learning across experimental conditions", 
+          title = "Predictions of money for learning", 
           header = FALSE,
@@
 
-## Model validation with RMSE
+## Model Validation
+
+Discuss model validation here...
 
@@
 
+### Define functions for R-squared, MSE, and RMSE
 RSQ <- function(model) {
-  return(summary(model)$r.squared)
+  result <- summary(model)$r.squared
+  return(formatNumber(result, 3))
 }
@@
 MSE <- function(error) {
-  return(mean(error^2))
+  result <- mean(error^2)
+  return(formatNumber(result, 3))  
 }
@@
 RMSE <- function(error) {
-  return(sqrt(mean(error^2))) 
+  result <- sqrt(mean(error^2))
+  return(formatNumber(result, 3)) 
 }
 
+```
+
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
+
+### Calculate R-squared, MSE, and RMSE for each model 
 vecModel <-
@@
 
+### Display the result in a table
 dfModelValid <-
   data.frame(vecModel, vecRSQ, vecMSE, vecRMSE) %>%
-  kable(caption = "Model validation",
+  kable(caption = "Results of model validation metrics",
         booktabs = TRUE,
@@
 # Model3 has the lowest RMSE among the 3 models => Model3 is the best!
+```
+
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
+
+### Calculate R-squared, MSE, and RMSE for each model
+vecModel_city <-
+  c("Model (1)", "Model (2)", "Model (3)", "Model (4)")
+
+vecRSQ_city <- 
+  c(RSQ(linReg1), RSQ(linReg2), RSQ(linReg3), RSQ(linReg4))
+
+vecMSE_city <-
+  c(MSE(linReg1$residuals), MSE(linReg2$residuals), MSE(linReg3$residuals),  MSE(linReg4$residuals))
+
+vecRMSE_city <-
+  c(RMSE(linReg1$residuals), RMSE(linReg2$residuals), RMSE(linReg3$residuals), RMSE(linReg4$residuals))
+
+### Display the result in a table
+dfModelValidCity <-
+  data.frame(vecModel_city, vecRSQ_city, vecMSE_city, vecRMSE_city) %>%
+  kable(caption = "Results of model validation metrics",
+        booktabs = TRUE,
+        col.names = c("Model", "R-squared", "MSE", "RMSE")) %>%
+  column_spec(column = 1, width = "4cm") %>%
+  column_spec(column = 2:4, width = "3cm")
+
+dfModelValidCity
 

### 2021-04-21 outputs/paper/paper.Rmd
Edit model evaluation tables

@@
           header = FALSE,
-          type = "latex")
+          type = "latex",
+          column.labels = c("Model (1)", "Model (2)", "Model (3)"),
+          model.numbers = FALSE)
 ```
@@
           type = "latex",
-          column.labels = c("Any", "Small", "Medium", "Large"),
+          column.labels = c("Model (4): Any", "Model (5): Small", "Model (6): Medium", "Model (7): Large"),
+          model.numbers = FALSE,
           font.size = "tiny")

### 2021-04-21 outputs/paper/paper.Rmd
Edit model formulae

@@
 
-This equation \@ref(eq:linRegModel1) is a model formula for the regression model 1.
+This equation \@ref(eq:linRegModel1) is a model formula for Model (1).
 
@@
 (\#eq:linRegModel1)
+Y \sim \beta_0 + \beta_1X_1 + \epsilon
+\end{equation}
+
+This equation \@ref(eq:linRegModel2) is a model formula for Model (2).
+
+\begin{equation}
+(\#eq:linRegModel2)
 Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \epsilon
@@
 
-This equation \@ref(eq:linRegModel2) is a model formula for the regression model 2.
-
-\begin{equation}
-(\#eq:linRegModel2)
-Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \epsilon
-\end{equation}
-
-This equation \@ref(eq:linRegModel3) is a model formula for the regression model 3.
+This equation \@ref(eq:linRegModel3) is a model formula for Model (3).
 
@@
 Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \beta_6X_6 + \epsilon
+\end{equation}
+
+This equation \@ref(eq:linRegModel4567) is a model formula for Model (4), (5), (6) and (7).
+
+\begin{equation}
+(\#eq:linRegModel4567)
+Y \sim \beta_0 + \beta_1X_1 + \epsilon
 \end{equation}

### 2021-04-21 outputs/paper/paper.Rmd
Edit model evaluation metrics

@@
 
+# No correlation coefficient > 0.9 
+# No multicollinearity
 ```
@@
 #### Beta ####
+# TODO: create a bar plot to show which variable affects the most 
+QuantPsyc::lm.beta(multiReg2)
 QuantPsyc::lm.beta(multiReg3)
@@
 ### VIF
+car::vif(multiReg2)
 car::vif(multiReg3)
+
 ### Tolerance
+1/car::vif(multiReg2)
 1/car::vif(multiReg3)

### 2021-04-22 outputs/paper/paper.Rmd
Edit continous variables for education level

@@
   data.frame(vecModel, vecRSQ, vecMSE, vecRMSE) %>%
-  kable(caption = "Results of model validation metrics",
+  kable(caption = "Results of model validation metrics for model group 1",
         booktabs = TRUE,
@@
 vecModel_city <-
-  c("Model (1)", "Model (2)", "Model (3)", "Model (4)")
+  c("Model (4)", "Model (5)", "Model (6)", "Model (7)")
 
@@
   data.frame(vecModel_city, vecRSQ_city, vecMSE_city, vecRMSE_city) %>%
-  kable(caption = "Results of model validation metrics",
+  kable(caption = "Results of model validation metrics for model group 2",
         booktabs = TRUE,

### 2021-04-22 scripts/01-data_cleaning.R

@@ -44,15 +44,15 @@ dfClean <-
                                 .default = 999)) %>%
   mutate(SchoolDegree = dplyr::recode(SchoolDegree,
                                 "no high school (secondary school)" = 0,
-                                "some high school" = 0,
-                                "high school diploma or equivalent (GED)" = 0,
-                                "trade, technical, or vocational training" = 0,
-                                "some college credit, no degree" = 1,
-                                "associate's degree" = 1,
-                                "bachelor's degree" = 2,
-                                "master's degree (non-professional)" = 3,
-                                "professional degree (MBA, MD, JD, etc.)" = 3,
-                                "Ph.D." = 4,
+                                "some high school" = 1,
+                                "high school diploma or equivalent (GED)" = 2,
+                                "trade, technical, or vocational training" = 2,
+                                "some college credit, no degree" = 3,
+                                "associate's degree" = 4,
+                                "bachelor's degree" = 5,
+                                "master's degree (non-professional)" = 6,
+                                "professional degree (MBA, MD, JD, etc.)" = 6,
+                                "Ph.D." = 7,
                                 .default = 999)) %>%
   ### Relocate columns
   dplyr::relocate(Gender, .before = Age) %>%

### 2021-04-22 outputs/paper/paper.Rmd
Add multicollinearity diagnostics table

@@
 
-```{r}
-#### Beta ####
-# TODO: create a bar plot to show which variable affects the most 
-QuantPsyc::lm.beta(multiReg2)
-QuantPsyc::lm.beta(multiReg3)
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
+#### Multicollinearity diagnostics ####
+# Check multicollinearity with Variance Inflation Factor (VIF) & Tolerance
+
+multicolDiagno <- function(mode, title) {
+  betaModel2 <- QuantPsyc::lm.beta(mode)
+  vifModel2 <- car::vif(mode)
+  tolModel2 <- 1/car::vif(mode)
+
+  dfMulticol <-
+    betaModel2 %>%
+    rbind(formatNumber(unname(betaModel2), 3)) %>%
+    rbind(formatNumber(unname(vifModel2), 3)) %>%
+    rbind(formatNumber(unname(unname(tolModel2)), 3)) %>%
+    cbind(c("B", "Beta", "VIF", "Tolerance"))
+    # dplyr::relocate(Metric, .before = CityPopulation) %>%
+    # dplyr::select(Metric, everything()) %>%
+    # kable()
+
+  ### Relocate 'Metric' column: alternative to 'dplyr::relocate()'
+  dfMulticol <- dfMulticol[-1,]
+  dfMulticol <- dfMulticol[,c(ncol(dfMulticol),1:ncol(dfMulticol)-1)]
+
+  kable(dfMulticol, 
+        caption = title,
+        booktabs = TRUE)
+}
 ```
 
-```{r}
-#### Check multicollinearity with Variance Inflation Factor (VIF) & Tolerance ####
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
+#### Multicollinearity diagnostics for Model (2) ####
+multicolDiagno(multiReg2, "Results of multicollinearity diagnostic metrics for Model (2)")
+```
 
-### VIF
-car::vif(multiReg2)
-car::vif(multiReg3)
-
-### Tolerance
-1/car::vif(multiReg2)
-1/car::vif(multiReg3)
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
+#### Multicollinearity diagnostics for Model (3) ####
+multicolDiagno(multiReg3, "Results of multicollinearity diagnostic metrics for Model (3)")
 ```
@@
 # Results
+```{r, include=FALSE}
+#### Beta ####
+# TODO: create a bar plot to show which variable affects the most with Beta
+```
 

### 2021-04-24 outputs/paper/paper.Rmd
Edit text in paper.Rmd

@@
 library(here)
-# install.packages("PerformanceAnalytics")
-library(PerformanceAnalytics)
 # install.packages("QuantPsyc")
@@
 
-```{r, echo=FALSE, warning=FALSE, message=FALSE}
-### Print correlation matrix
-PerformanceAnalytics::chart.Correlation(dfNewCoders, 
-                                        histogram = TRUE, 
-                                        pch = 19)
-```
-
 # Model
@@
 
-This equation \@ref(eq:linRegModel1) is a model formula for Model (1).
+In the earlier section, I ran a correlation matrix to identify the correlation of each variable and the significance of the relationship between the dependent variable (MoneyForLearning) and other dependents variables.
+But, I was not able to estimate how much the independent variables impact the dependent variable from the correlation analysis.
+In this section, I will examine effects of the dependent variables on the dependent variable, focusing on one of the dependent variables: Income.
+The two main questions that I set out to answer in this section are: (1) How do beginner programmers' income affect the cost of their education to learn code?
+and (2) Will the effects change according to the population of the city where they live in.
+To obtain the answer for the first question, I used a simple linear regression model (Model 1) and multiple linear regression models (Model 2 and 3).
+All these three models use MoneyForLearning (the cost of their education to learn code) as a dependent variable.
+Model 1 contains only one independent variable, which is Income (see Model \@ref(eq:linRegModel1)); otherwise, Model 3 uses all the independent options except for CommuteTime: Gender, Age, CityPopulation, Income, MonthsProgramming, and SchoolDegree (see Model \@ref(eq:linRegModel3)).
+And, Model 2 uses the same independent variables, excluding Gender and Age.
+For the second question about the effects of the population of the city where the programmers reside, I used four simple linear regression models (see \@ref(eq:linRegModel2)).
+Like Model 1, all these models use MoneyForLearning as a dependent variable and Income as an independent variable (see Model \@ref(eq:linRegModel1)).
+But, the observations were grouped by the population size of the programmers.
+Model 4 contains any size of population; and Model 5,6, and 7 are the small (less than 100,000), medium (between 100,000 and 1 million), and large (more than 1 million) size population.
 
@@
 
-This equation \@ref(eq:linRegModel2) is a model formula for Model (2).
-
 \begin{equation}
@@
 
-This equation \@ref(eq:linRegModel3) is a model formula for Model (3).
-
 \begin{equation}
@@
 Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \beta_6X_6 + \epsilon
-\end{equation}
-
-This equation \@ref(eq:linRegModel4567) is a model formula for Model (4), (5), (6) and (7).
-
-\begin{equation}
-(\#eq:linRegModel4567)
-Y \sim \beta_0 + \beta_1X_1 + \epsilon
 \end{equation}

### 2021-04-24 outputs/paper/paper.Rmd
Edit text in paper.Rmd

@@
 and (2) Will the effects change according to the population of the city where they live in.
-To obtain the answer for the first question, I used a simple linear regression model (Model 1) and multiple linear regression models (Model 2 and 3).
+To obtain the answer for the first question, I used a simple linear regression model (Equation \@ref(eq:linRegModel1)) and multiple linear regression models (Equation \@ref(eq:linRegModel2) and \@ref(eq:linRegModel3)).
 All these three models use MoneyForLearning (the cost of their education to learn code) as a dependent variable.
-Model 1 contains only one independent variable, which is Income (see Model \@ref(eq:linRegModel1)); otherwise, Model 3 uses all the independent options except for CommuteTime: Gender, Age, CityPopulation, Income, MonthsProgramming, and SchoolDegree (see Model \@ref(eq:linRegModel3)).
+Model 1 contains only one independent variable, which is Income (see Equation \@ref(eq:linRegModel1)); otherwise, Model 3 uses all the independent options except for CommuteTime: Gender, Age, CityPopulation, Income, MonthsProgramming, and SchoolDegree (see Equation \@ref(eq:linRegModel3)).
+As mentioned in the Correlation Analysis section, the CommuteTime (a commuting time) variable does not significantly affect the response variable, so it is excluded from the regression models.
 And, Model 2 uses the same independent variables, excluding Gender and Age.
-For the second question about the effects of the population of the city where the programmers reside, I used four simple linear regression models (see \@ref(eq:linRegModel2)).
-Like Model 1, all these models use MoneyForLearning as a dependent variable and Income as an independent variable (see Model \@ref(eq:linRegModel1)).
+For the second question about the effects of the population of the city where the programmers reside, I used four simple linear regression models (see Equation \@ref(eq:linRegModel2)).
+Like Model 1, all these models use MoneyForLearning as a dependent variable and Income as an independent variable (see Equation \@ref(eq:linRegModel1)).
 But, the observations were grouped by the population size of the programmers.
@@
 \end{equation}
+
+## Data Preprocessing
 
@@
 # Appendix {-}
+## Survey questions {-}
+
+Q. [Age] How old are you?
+
+* Type: integer
+
+Q. [CityPopulation] About how many people live in your city?
+
+* Type: string
+
+* Options:
+  1. less than 100,000
+  2. between 100,000 and 1 million
+  3. more than 1 million
+
+Q. [CommuteTime] About how many minutes does it take you to get to work each day?
+
+* Type: string
+
+* Options:
+  1. I work from home
+  2. Less than 15 minutes
+  3. 15 to 29 minutes
+  4. 30 to 44 minutes
+  5. 45 to 60 minutes
+  6. More than 60 minutes
+
+Q. [Gender] What's your gender?
+
+* Type: string
+
+* Options:
+  1. male
+  2. female
+
+Q. [Income] About how much money did you make last year, in US dollars?
+
+* Type: integer
+
+Q. [MoneyForLearning] Aside from university tuition, about how much money have you spent on learning to code so far, in US dollars?
+
+* Type: integer
+
+Q. [MonthsProgramming] About how many months have you been programming for?
+
+* Type: integer
+
+Q. [SchoolDegree] What's the highest degree or level of school you have completed?
+
+* Type: string
+
+* Options:
+  1. no high school (secondary school)
+  2. some high school
+  3. high school diploma or equivalent (GED)
+  4. trade, technical, or vocational training
+  5. some college credit, no degree
+  6. associate's degree
+  7. bachelor's degree
+  8. master's degree (non-professional)
+  9. professional degree (MBA, MD, JD, etc.)
+  10. Ph.D.
 

### 2021-04-24 outputs/paper/paper.Rmd
Edit text in paper.Rmd

@@
 and (2) Will the effects change according to the population of the city where they live in.
+
 To obtain the answer for the first question, I used a simple linear regression model (Equation \@ref(eq:linRegModel1)) and multiple linear regression models (Equation \@ref(eq:linRegModel2) and \@ref(eq:linRegModel3)).
@@
 ## Data Preprocessing
+
+As explained in the Data section, categorical variables were converted to continuous variables for the linear regression models.
+For example, the SchoolDegree variable (the level of education) was a categorical variable with character values.
+So, I converted the variable into a variable with numeric values, using the `dplyr` package.
+A complete list of survey questions and response options for each question can be found in the Appendix.
+Since the MoneyForLearning variable (the level of education) was not only categorical but also ordered and ranked in the original dataset, I converted the variable into a variable with numeric values.
+Also, I merged some of the response options of the variable.
+For instance, it is somewhat hard to say that a high school diploma or equivalent (GED) is higher than trade, technical, or vocational training, and a professional degree, such as MBA, MD, or JD, is higher than a non-professional master's degree.
+So, I merged the options, using the `recode` function of the `dplyr` package [@cityDplyr].
 

### 2021-04-24 outputs/paper/paper.Rmd
Edit text in paper.Rmd

@@
 
-Discuss model validation here...
+I will use Mean Square Error (MSE) and Root Mean Square Error (RMSE) to evaluate the accuracy of the model.
+As the name implies, MSE is defined as the mean of the square of the residuals obtained from a regression model, and RMSE is the square root of MSE [@citeHolmes].
+I will use the residuals which are the results of the `lm` function to calculate MSE and RMSE of the models.
+Firstly, I will calculate the square of the residuals, and then computed the mean of the squared value for MSE (see Equation \@ref(eq:mse)).
+Secondly, for RMSE, I will use the `sqrt` function to calculate the square root of MSE (see Equation \@ref(eq:rmse)).
+Once I obtain the results of MSE and RMSE, I will compare them to see how accurately the models predict the response.
+
+\begin{equation}
+(\#eq:mse)
+MSE = \frac{1}{N}\sum_{i=1}^{N} (residuals_{i})^2
+\end{equation}
+
+\begin{equation}
+(\#eq:rmse)
+RMSE = \sqrt{\frac{1}{N}\sum_{i=1}^{N} (residuals_{i})^2}
+\end{equation}
 

### 2021-04-24 outputs/paper/paper.Rmd
Edit text in paper.Rmd

@@
 (\#eq:mse)
-MSE = \frac{1}{N}\sum_{i=1}^{N} (residuals_{i})^2
+MSE = \frac{1}{N}\sum_{i=1}^{N} (residual_{i})^2
 \end{equation}
@@
 (\#eq:rmse)
-RMSE = \sqrt{\frac{1}{N}\sum_{i=1}^{N} (residuals_{i})^2}
+RMSE = \sqrt{\frac{1}{N}\sum_{i=1}^{N} (residual_{i})^2}
 \end{equation}
+
+Since two multiple linear regression models (Model 2 and 3) are used in the first group of regression models, I will check if multicollinearity exists in these regression models, using variance inflation factor (VIF) and tolerance.
+I will use the `car` package to calculate the value of VIF and tolerance for each model [@citeCar].
+Also, I will identify how much each of the independent variables affects the dependent variable with the standardized regression coefficients (beta).
+the `QuantPsyc` package will be used to compute the beta value [@citeQuanPsy].
+
+# Results
+```{r, include=FALSE}
+#### Beta ####
+# TODO: create a bar plot to show which variable affects the most with Beta
+```
 
@@
 
-# Results
-```{r, include=FALSE}
-#### Beta ####
-# TODO: create a bar plot to show which variable affects the most with Beta
-```
-
 # Discussion

### 2021-04-25 outputs/paper/paper.Rmd
Edit text in paper.Rmd

@@
 
-```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
-#### Multiple regression analysis ####
+## Model Validation
+
+I will use Mean Square Error (MSE) and Root Mean Square Error (RMSE) to evaluate the accuracy of the model.
+As the name implies, MSE is defined as the mean of the square of the residuals obtained from a regression model, and RMSE is the square root of MSE [@citeHolmes].
+I will use the residuals which are the results of the `lm` function to calculate MSE and RMSE of the models.
+Firstly, I will calculate the square of the residuals, and then computed the mean of the squared value for MSE (see Equation \@ref(eq:mse)).
+Secondly, for RMSE, I will use the `sqrt` function to calculate the square root of MSE (see Equation \@ref(eq:rmse)).
+Once I obtain the results of MSE and RMSE, I will compare them to see how accurately the models predict the response.
+
+\begin{equation}
+(\#eq:mse)
+MSE = \frac{1}{N}\sum_{i=1}^{N} (residual_{i})^2
+\end{equation}
+
+\begin{equation}
+(\#eq:rmse)
+RMSE = \sqrt{\frac{1}{N}\sum_{i=1}^{N} (residual_{i})^2}
+\end{equation}
+
+Since two multiple linear regression models (Model 2 and 3) are used in the first group of regression models, I will check if multicollinearity exists in these regression models, using variance inflation factor (VIF) and tolerance.
+I will use the `car` package to calculate the values of VIF and tolerance for each model [@citeCar].
+Also, I will identify how much each of the independent variables affects the dependent variable with the standardized regression coefficients (beta).
+the `QuantPsyc` package will be used to compute the beta value [@citeQuanPsy].
+
+# Results
+
+## Results of Regression Model
+
+All the regression models in the first group of the models had p-values of F-statistic lower than a significance level of 0.05 (see Table 4).
+And, each of the independent variables also had a p-value of less than 0.05 except for the SchoolDegree variable in Model 3.
+This can be interpreted that all the independent variables excluding the SchoolDegree variable have an impact on the response variable (MoneyForLearning), and the level of education (SchoolDegree) is not statistically significant on the response variable with holding all other variables.
+However, the SchoolDegree variable becomes statistically significant if the Gender and Age variables are excluded from the regression model.
+
+```{r tabLinRegModel1, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
+#### Linear regression models (Group 1) ####
 
@@
 
-```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
-#### Multiple regression analysis (by city population) ####
+The second group of regression models to examine the effects of the population of the city where the programmers reside shows that all the models have statistically significant p-values of F-statistic except for Model 5, the model for the small city with less than 100,000 residents (see Table 5).
+In other words, beginner programmers' income affects the cost of their education to learn code; however, their income does not affect the cost when the model contains only observations from the small city.
+
+```{r tabLinRegModel2, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
+#### Linear regression models (Group 2) ####
 dfSmCity <-
@@
 
-```
-
-## Model Validation
-
-I will use Mean Square Error (MSE) and Root Mean Square Error (RMSE) to evaluate the accuracy of the model.
-As the name implies, MSE is defined as the mean of the square of the residuals obtained from a regression model, and RMSE is the square root of MSE [@citeHolmes].
-I will use the residuals which are the results of the `lm` function to calculate MSE and RMSE of the models.
-Firstly, I will calculate the square of the residuals, and then computed the mean of the squared value for MSE (see Equation \@ref(eq:mse)).
-Secondly, for RMSE, I will use the `sqrt` function to calculate the square root of MSE (see Equation \@ref(eq:rmse)).
-Once I obtain the results of MSE and RMSE, I will compare them to see how accurately the models predict the response.
-
-\begin{equation}
-(\#eq:mse)
-MSE = \frac{1}{N}\sum_{i=1}^{N} (residual_{i})^2
-\end{equation}
-
-\begin{equation}
-(\#eq:rmse)
-RMSE = \sqrt{\frac{1}{N}\sum_{i=1}^{N} (residual_{i})^2}
-\end{equation}
-
-Since two multiple linear regression models (Model 2 and 3) are used in the first group of regression models, I will check if multicollinearity exists in these regression models, using variance inflation factor (VIF) and tolerance.
-I will use the `car` package to calculate the value of VIF and tolerance for each model [@citeCar].
-Also, I will identify how much each of the independent variables affects the dependent variable with the standardized regression coefficients (beta).
-the `QuantPsyc` package will be used to compute the beta value [@citeQuanPsy].
-
-# Results
-```{r, include=FALSE}
-#### Beta ####
-# TODO: create a bar plot to show which variable affects the most with Beta
 ```

### 2021-04-25 outputs/paper/paper.Rmd
Edit text in paper.Rmd

@@
 
+## Results of Model Validation
+
+Table \@ref(tab:tab6) is the results of MSE and RMSE of the first group consisting of Model 1, 2, and 3.
+Among these three models, Model 3 containing all independent variable options has the lowest value of RMSE.
+So, it can be said that Model 3 predicts the response variable more accurately with holding all independent variables, compared to Model 1 and 2 which contains the Income variable or excludes the Age and Gender variables.
+
+Table \@ref(tab:tab7) is the results of MSE and RMSE of the second group consisting of Model 4, 5, 6, and 7.
+Among these four models, Model 5 (the regression model for the small city) has the lowest MSE and RMSE.
+However, as explained earlier, the p-values of F-statistic for the model was higher than a significance level of 0.05, which means the model is not statistically significant.
+The most accurate regression model excluding Model 5 among the four models was Model 4 which includes cities of all sizes, followed by Model 7.
+
+Model 3 and 4 are the most accurate model in each of the groups.
+However, as can be seen in Table \@ref(tab:tab6) and \@ref(tab:tab7), all the models have an extremely low R-squared value, which is very close to 0.
+In other words, the accuracy of the regression models is intensively low because the residuals (the difference between the measured values and the predicted values of the models) are high.
+Thus, it is hard to say that those six variables (Gender, Age, CityPopulation, Income, MonthsProgramming, and SchoolDegree) have a significant effect on education costs of beginner programmers to learn to code.
+
 ```{r tabLinRegModel2, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
@@
 
-```{r, echo=FALSE, warning=FALSE, message=FALSE}
+```{r tab6, echo=FALSE, warning=FALSE, message=FALSE}
 
@@
 
-```{r, echo=FALSE, warning=FALSE, message=FALSE}
+```{r tab7, echo=FALSE, warning=FALSE, message=FALSE}
 
@@
 
-```{r, echo=FALSE, warning=FALSE, message=FALSE}
+```{r tab8, echo=FALSE, warning=FALSE, message=FALSE}
 #### Multicollinearity diagnostics for Model (2) ####
@@
 
-```{r, echo=FALSE, warning=FALSE, message=FALSE}
+```{r tab9, echo=FALSE, warning=FALSE, message=FALSE}
 #### Multicollinearity diagnostics for Model (3) ####

### 2021-04-25 outputs/paper/paper.Rmd
Edit text in paper.Rmd

@@
 
-## Results of Model Validation
-
-Table \@ref(tab:tab6) is the results of MSE and RMSE of the first group consisting of Model 1, 2, and 3.
-Among these three models, Model 3 containing all independent variable options has the lowest value of RMSE.
-So, it can be said that Model 3 predicts the response variable more accurately with holding all independent variables, compared to Model 1 and 2 which contains the Income variable or excludes the Age and Gender variables.
-
-Table \@ref(tab:tab7) is the results of MSE and RMSE of the second group consisting of Model 4, 5, 6, and 7.
-Among these four models, Model 5 (the regression model for the small city) has the lowest MSE and RMSE.
-However, as explained earlier, the p-values of F-statistic for the model was higher than a significance level of 0.05, which means the model is not statistically significant.
-The most accurate regression model excluding Model 5 among the four models was Model 4 which includes cities of all sizes, followed by Model 7.
-
-Model 3 and 4 are the most accurate model in each of the groups.
-However, as can be seen in Table \@ref(tab:tab6) and \@ref(tab:tab7), all the models have an extremely low R-squared value, which is very close to 0.
-In other words, the accuracy of the regression models is intensively low because the residuals (the difference between the measured values and the predicted values of the models) are high.
-Thus, it is hard to say that those six variables (Gender, Age, CityPopulation, Income, MonthsProgramming, and SchoolDegree) have a significant effect on education costs of beginner programmers to learn to code.
-
 ```{r tabLinRegModel2, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
@@
 ```
+
+## Results of Model Validation
+
+Table \@ref(tab:tab6) is the results of MSE and RMSE of the first group consisting of Model 1, 2, and 3.
+Among these three models, Model 3 containing all independent variable options has the lowest value of RMSE.
+So, it can be said that Model 3 predicts the response variable more accurately with holding all independent variables, compared to Model 1 and 2 which contains the Income variable or excludes the Age and Gender variables.
+
+Table \@ref(tab:tab7) is the results of MSE and RMSE of the second group consisting of Model 4, 5, 6, and 7.
+Among these four models, Model 5 (the regression model for the small city) has the lowest MSE and RMSE.
+However, as explained earlier, the p-values of F-statistic for the model was higher than a significance level of 0.05, which means the model is not statistically significant.
+The most accurate regression model excluding Model 5 among the four models was Model 4 which includes cities of all sizes, followed by Model 7.
+
+Model 3 and 4 are the most accurate model in each of the groups.
+However, as can be seen in Table \@ref(tab:tab6) and \@ref(tab:tab7), all the models have an extremely low R-squared value, which is very close to 0.
+In other words, the accuracy of the regression models is intensively low because the residuals (the difference between the measured values and the predicted values of the models) are high.
+Thus, it is hard to say that those six variables (Gender, Age, CityPopulation, Income, MonthsProgramming, and SchoolDegree) have a significant effect on education costs of beginner programmers to learn to code.
 
@@
 dfModelValid
-
-# If R-squared is closer to 0 = Good!
-# Model3 has the lowest RMSE among the 3 models => Model3 is the best!
 ```
@@
 ```
+
+Table \@ref(tab:tab8) is the results of the multicollinearity diagnostic test for Model (2).
+The results show that the MonthsProgramming variable has the highest beta value, which means the independent variable has the most significant effect on the dependent variable (MoneyForLearning) among those four independent variables included in the regression model.
+However, all the beta values of the independent variables are extremely low and close to 0, meaning that their effects are not significant.
+All the VIF and tolerance of each variable are very close to 1, which means there is almost no multicollinearity; a VIF of 10 or higher, or tolerance close 0 indicates that the model might have multicollinearity [@citeWilliams].
+
+Table \@ref(tab:tab9) is the results of the multicollinearity diagnostic test for Model (3).
+The variable which has the highest beta value is the CityPopulation variable, which means the size of the city has the most significant effect on education costs of beginner programmers to learn to code among those six independent variables used in the regression model.
+Like the results of the test for Model (2), Model (3) also does not have significant multicollinearity; the VIF and tolerance of each variable of the model are in an acceptable range.
+In concussion, there is no significant multicollinearity found in both Model (2) and (3).
+However, all the regression models have an extremely low R-squared value, meaning the regression models have poor accuracy of prediction.
 

### 2021-04-26 outputs/paper/paper.Rmd
Edit text in paper.Rmd

@@
 
+\newpage
+
 # Discussion
-```{r, include=FALSE}
-#### TODO's ####
-# Write at least 2.5 pages for the Discussion section
-# Weaknesses and next steps
-```
+
+## Summary
+In this paper, I examine potential factors that may affect costs of beginner programmers to learn to code aside from post secondary education based on the online survey run by freeCodeCamp in 2017.
+Firstly, I chose eight variables, including the dependent variable (educational expenses of the programmers) from the original dataset.
+Secondly, I ran a correlation matrix for all the independent variables to examine how closely they are related with the dependent variable.
+Thirdly, I used linear regression models to determine influence factors on the dependent variable from the independent variables excluding a commuting time which was confirmed not to have the correlation with the dependent variable.
+Fourthly, I ran two groups of linear regression models to examine effects of the dependent variables on the dependent variable: the first group was for identifying how programmers’ income affects their educational costs to learn to code and the second group was for looking into how the effect of their income changes according to the population of the city where the programmers live in.
+Finally, I evaluated the models using R-squared, MSE and RMSE scores of each model.
+Also, I used beta, VIF, and tolerance scores to check if there is multicollinearity in the multiple linear regression models.
+
+Summary of the findings are as follows: (1) The statistical relationship exists between all the independent variables excluding a commuting time and new coders’ expenses to learn to code aside from their college or university tuition, (2) The level of education is not statistically significant on the new coders’ expenses to learn to code, (3) Their income is statistically significant on the costs; but, the prediction model can become less accurate if the model includes only response data of the programmers from the small city, (4) There is no multicollinearity found in the multiple linear regression models, and lastly (5) All the models used in this paper have an extremely low R-squared score, which means that it is difficult to argue that those selected independent variable significantly affect the independent variable.
+In short, it can be argued that there is a correlation between each of the independent variables (the level of education, the size of city, a commuting time, income, and learning time) and the dependent variable (the cost of learning to code); however, there is no significant causal relationship between the variables.
+
+## Casuality
 

### 2021-04-26 outputs/paper/paper.Rmd
Edit text in paper.Rmd

@@
 ## Casuality
+In addition to the low R-squared scores, there is another reason that causality cannot be explained from the regression models.
+In reality, there will be plenty of factors that actually affect beginner programmers’ expenses to learn to code besides those selected seven variables.
+For example, there might be some institutions where the programmers can learn to code near their home, or some of them might be heavily exposed to online advertisements of some online-learning platforms that teach programming.
+In other words, realistically, it is almost impossible to measure all the variables happening in the large world and include them in the model.
+However, we can always measure which variables are significant and determine the most appropriate variables to make a model closer to the reality.
+For future studies, I suggest running the same analysis process, from the correlation analysis to linear regression models and model validation, with other variables that are not covered in this paper.
+Also, surveys of other years can be used to compare the results of this analysis.
 

### 2021-04-26 outputs/paper/paper.Rmd
Edit text in paper.Rmd

@@
 ---
-title: "The Impact of Educational Expenses of New Coders"
-subtitle: "The Factors Affecting Education Costs of Beginner Programmers to Learn to Code aside from University Tuition"
+title: "What Makes New Coders Spend More Money"
+subtitle: "The Factors Affecting Beginner Programmers' Expenses to Learn to Code"
 author: "Bongju Yoo"
-thanks: "https://github.com/bonjwow/new-coders"
+thanks: "Code and data are available at: [https://github.com/bonjwow/new-coders]"
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: ""
+abstract: "I examine potential factors that may affect education costs of new coders to learn to code aside from their post secondary education based on the responses of the online survey run by freeCodeCamp in 2017.
+I use a correlation matrix and linear regression models to see if there is a correlation and causal relationship between the potential factors and the costs of learning to code.
+The results of the analysis show that a commuting time to work and the level of education do not affect educational expenditure of new coders to learn to code.
+It is also found that there is a correlation between each of the independent variables and the dependent variable, excluding a commuting time; however, there is no significant causal relationship between the variables.
+\\par \\textbf{Keywords:} Programmers, Coder, Education Costs, Coding, Online education, Open education"
 output:
@@
 
-Firstly, I processed correlation analysis to identify the relationship between each independent variable and dependent variable (education costs) pair and found that all the pairs have a positive linear relationship except for commuting time.
-Secondly, I used multiple linear regression to determine the statistical significance of the factors.
-The result of the analysis shows that commuting time is not statistically significant.
-Interestingly, education background is also not statistically significant associated with educational expenses of beginner programmers.
-Other variables, such as the size of city, income, and learning time, have a statistical significance on the costs.
-
-This analysis shows that beginner programmers living in small towns and/or low-income households are likely to spend less money on learning to code aside from university tuition than those who live in bigger cities and/or high-income households.
+Firstly, I processed correlation analysis to identify the relationship between each independent variable and dependent variable (the costs of learning to code) pair and found that all the pairs have a positive linear relationship except for a commuting time.
+Secondly, I used a combination of simple linear regression models and multiple linear regressions to determine the statistical significance of the factors.
+The result of the analysis shows that the level of education is not statistically significant on the new coders’ expenses to learn to code.
+Also, the analysis shows that the income of the programmers is statistically significant on the costs.
+So, it can be argued that those beginner programmers living in small towns and/or low-income households are likely to spend less money on learning to code aside from college or university tuition than those who live in bigger cities and/or high-income households.
 It is assumed that there is still a lack of educational resources for new coders living in rural areas and/or low-income households.
 Free online learning platforms such as freeCodeCamp can be a great resource of education for the coders.
+Unfortunately, all the regression models used to examine the effect of new coders' income had an extremely low R-squared score.
+So, it fails to compute the average of predicted costs of the programmers with specific values of the independent variable(s).
 

### 2021-04-26 outputs/paper/paper.Rmd
Edit text in paper.Rmd

@@
 author: "Bongju Yoo"
-thanks: "Code and data are available at: [https://github.com/bonjwow/new-coders]"
+thanks: "Code and data are available at: [github.com/bonjwow/new-coders](https://github.com/bonjwow/new-coders)."
 date: "`r format(Sys.time(), '%d %B %Y')`"
@@
 library(dplyr)
-library(janitor)
 library(stargazer)
-library(psych)
 # install.packages("here")

### 2021-04-26 outputs/paper/paper.Rmd
Edit text in paper.Rmd

@@
 
+## Software Used {-}
+This paper is written in Rmarkdown [@citeRmarkdown] and `bookdown` [@citeBookdown], and printed by the `knitr` package [@citeKnitr].
+The `here` package was used to set the path to the project folder [@citeHere].
+And, the `kableExtra` [@citeKable] and `stargazer` [@citeStargazer] packages were used to crate tables.
+
 \newpage

### 2021-04-27 outputs/paper/paper.Rmd
Fix typos

@@
 With an increasing interest in computer programming and the growth of coding related jobs, more and more people invest their time and money in taking programming courses [@citeHughes].
-In this paper, I examine some of the factors that may affect educational expenses of new coders or entry-level programmers aside from university tuition, mainly focusing on the level of education, the size of city, commuting time, income, and learning time.
+In this paper, I examine some of the factors that may affect educational expenses of new coders or entry-level programmers aside from their college/university tuition, mainly focusing on the level of education, the size of city, commuting time, income, and learning time.
 Approximately 20,000 beginner programmers had participated in the survey [@citeSurvey2017].
@@
 Also, the analysis shows that the income of the programmers is statistically significant on the costs.
-So, it can be argued that those beginner programmers living in small towns and/or low-income households are likely to spend less money on learning to code aside from college or university tuition than those who live in bigger cities and/or high-income households.
+So, it can be argued that those beginner programmers living in small towns and/or low-income households are likely to spend less money on learning to code aside from their post secondary education costs than those who live in bigger cities and/or high-income households.
 It is assumed that there is still a lack of educational resources for new coders living in rural areas and/or low-income households.
-Free online learning platforms such as freeCodeCamp can be a great resource of education for the coders.
+Free online learning platforms such as `freeCodeCamp` can be a great resource of education for the coders.
 Unfortunately, all the regression models used to examine the effect of new coders' income had an extremely low R-squared score.
@@
 To create the correlation matrix, I used a custom function written by Stefan Eng [@citeEng].
-His function contains the `Hmisc` package’s `rcorr` function to calculate the correlations with the p-values and display starts based on the significance level of each cell when the value is lower than a specific level [@citeHmisc].
-Along with his custom to compute the correlation matrix, I used the `kable` package to print out the result in a table format [@citeKable].
+His function contains the `Hmisc` package’s `rcorr` function to calculate the correlations with the p-values and display stars based on the significance level of each cell when the value is lower than a specific level [@citeHmisc].
+Along with his custom function to compute the correlation matrix, I used the `kable` package to print out the result in a table format [@citeKable].
 As can be seen in Table \@ref(tab:tabCorrAnalysis), the result of the correlation matrix shows that all independent variables have a positive significant relationship with the dependent variable, MoneyForLearning, except for CommuteTime.
-This can be interpreted that a commuting time to work does not affect educational expenditure of new coders aside from their post-secondary education cost.
+This can be interpreted that a commuting time to work does not affect educational expenditure of new coders aside from their post-secondary education costs.
 
@@
 The two main questions that I set out to answer in this section are: (1) How do beginner programmers' income affect the cost of their education to learn code?
-and (2) Will the effects change according to the population of the city where they live in.
+and (2) Will the effects change according to the population of the city where they live in?
 
@@
 But, the observations were grouped by the population size of the programmers.
-Model 4 contains any size of population; and Model 5,6, and 7 are the small (less than 100,000), medium (between 100,000 and 1 million), and large (more than 1 million) size population.
+Model 4 contains any size of population; and Model 5, 6, and 7 are the small (less than 100,000), medium (between 100,000 and 1 million), and large (more than 1 million) size population.
 
@@
 A complete list of survey questions and response options for each question can be found in the Appendix.
-Since the MoneyForLearning variable (the level of education) was not only categorical but also ordered and ranked in the original dataset, I converted the variable into a variable with numeric values.
+Since the SchoolDegree variable was not only categorical but also ordered and ranked in the original dataset, I converted the variable into a variable with numeric values.
 Also, I merged some of the response options of the variable.
@@
 I will use the residuals which are the results of the `lm` function to calculate MSE and RMSE of the models.
-Firstly, I will calculate the square of the residuals, and then computed the mean of the squared value for MSE (see Equation \@ref(eq:mse)).
+Firstly, I will calculate the square of the residuals, and then compute the mean of the squared value for MSE (see Equation \@ref(eq:mse)).
 Secondly, for RMSE, I will use the `sqrt` function to calculate the square root of MSE (see Equation \@ref(eq:rmse)).
@@
 
-Since two multiple linear regression models (Model 2 and 3) are used in the first group of regression models, I will check if multicollinearity exists in these regression models, using variance inflation factor (VIF) and tolerance.
+R-squared, MSE, and RMSE scores can be calculated using the `evaluationMetrics` package that I developed. The instruction to install and use the package can be found in the Appendix.
+
+Since two multiple linear regression models (Model 2 and 3) are used in the first group of regression models, I will check if multicollinearity exists in these regression models, using Variance Inflation Factor (VIF) and tolerance.
 I will use the `car` package to calculate the values of VIF and tolerance for each model [@citeCar].
@@
 The second group of regression models to examine the effects of the population of the city where the programmers reside shows that all the models have statistically significant p-values of F-statistic except for Model 5, the model for the small city with less than 100,000 residents (see Table 5).
-In other words, beginner programmers' income affects the cost of their education to learn code; however, their income does not affect the cost when the model contains only observations from the small city.
+In other words, beginner programmers' income affects the cost of their education to learn to code; however, their income does not affect the cost when the model contains only observations from the small city.
 
@@
 
-Model 3 and 4 are the most accurate model in each of the groups.
+Model 3 and 4 are the most accurate models in each of the groups.
 However, as can be seen in Table \@ref(tab:tab6) and \@ref(tab:tab7), all the models have an extremely low R-squared value, which is very close to 0.
@@
 ## Summary
-In this paper, I examine potential factors that may affect costs of beginner programmers to learn to code aside from post secondary education based on the online survey run by freeCodeCamp in 2017.
+In this paper, I examine potential factors that may affect costs of beginner programmers to learn to code aside from their post secondary education costs based on the online survey run by `freeCodeCamp` in 2017.
 Firstly, I chose eight variables, including the dependent variable (educational expenses of the programmers) from the original dataset.
@@
 Thirdly, I used linear regression models to determine influence factors on the dependent variable from the independent variables excluding a commuting time which was confirmed not to have the correlation with the dependent variable.
-Fourthly, I ran two groups of linear regression models to examine effects of the dependent variables on the dependent variable: the first group was for identifying how programmers’ income affects their educational costs to learn to code and the second group was for looking into how the effect of their income changes according to the population of the city where the programmers live in.
+Fourthly, I ran two groups of linear regression models to examine effects of the dependent variables on the dependent variable: the first group was for identifying how programmers’ income affects their educational costs to learn to code, and the second group was for looking into how the effect of their income changes according to the population of the city where the programmers live in.
 Finally, I evaluated the models using R-squared, MSE and RMSE scores of each model.
@@
 
-Summary of the findings are as follows: (1) The statistical relationship exists between all the independent variables excluding a commuting time and new coders’ expenses to learn to code aside from their college or university tuition, (2) The level of education is not statistically significant on the new coders’ expenses to learn to code, (3) Their income is statistically significant on the costs; but, the prediction model can become less accurate if the model includes only response data of the programmers from the small city, (4) There is no multicollinearity found in the multiple linear regression models, and lastly (5) All the models used in this paper have an extremely low R-squared score, which means that it is difficult to argue that those selected independent variable significantly affect the independent variable.
+Summary of the findings are as follows: (1) The statistical relationship exists between all the independent variables excluding a commuting time and new coders’ expenses to learn to code aside from their college or university tuition fee, (2) The level of education is not statistically significant on the new coders’ education costs to learn to code, (3) Their income is statistically significant on the costs; but, the prediction model can become less accurate if the model includes only response data of the programmers from the small city, (4) There is no multicollinearity found in the multiple linear regression models, and lastly (5) All the models used in this paper have an extremely low R-squared score, which means that it is difficult to argue that those selected independent variable significantly affect the independent variable.
 In short, it can be argued that there is a correlation between each of the independent variables (the level of education, the size of city, a commuting time, income, and learning time) and the dependent variable (the cost of learning to code); however, there is no significant causal relationship between the variables.
@@
 ## Casuality
-In addition to the low R-squared scores, there is another reason that causality cannot be explained from the regression models.
+In addition to the low R-squared scores, there is another reason that causality cannot be explained from the regression models used in this paper.
 In reality, there will be plenty of factors that actually affect beginner programmers’ expenses to learn to code besides those selected seven variables.
@@
 For future studies, I suggest running the same analysis process, from the correlation analysis to linear regression models and model validation, with other variables that are not covered in this paper.
-Also, surveys of other years can be used to compare the results of this analysis.
+Also, the New Coder surveys of other years can be used to compare the results of this analysis.
 
@@
 # Appendix {-}
-## Survey questions {-}
+
+## Instruction for the 'evaluationMetrics' package {-}
+1. Install the package
+```
+library(devtools)
+install_github("bonjwow/evaluation-metrics")
+```
+
+2. Calculate the R-squared, MSE, or RMSE by parsing the fitted linear regression model. You may also set the number of decimal places to display by parsing the number that you want.
+
+Examples:
+```
+### Export sample dataset
+data(iris)
+linRegIris <- lm(Petal.Width ~ Petal.Length, data=iris)
+
+### Calculate R-squared
+print(evaluationMetrics::RSQ(linRegIris, decimal=3))
+
+### Calculate MSE
+print(evaluationMetrics::MSE(linRegIris, decimal=3))
+
+### Calculate RMSE
+print(evaluationMetrics::RMSE(linRegIris, decimal=3))
+```
+
+## Survey Questions {-}
 
@@
 
-## Software Used {-}
+## Other Software Used {-}
 This paper is written in Rmarkdown [@citeRmarkdown] and `bookdown` [@citeBookdown], and printed by the `knitr` package [@citeKnitr].
